---
title: "Untitled"
author: "Jorge Moncayo"
date: "18/1/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmdformats)
library(tidyverse)
library(urltools)
library(lubridate)
library(dplyr)
library(DT)
library(skimr)

load("limni2.rda")

limni2 <-  limni %>% 
  filter(territorial %in% c("Tahamíes"))

limni2$Year <- format(as.Date(limni2$fechas), "%Y")

p <-  ggplot(limni2, mapping = aes(x = Year, y = nivel, 
                                  color = Year)) +
  geom_boxplot() +
  facet_wrap(~municipios, scales = "free", nrow = 2)
```

```{r}
p
```


